---
title: "STAT 517 Final Project"
author: "Vignesh J Muralidharan"
date: "November 1, 2018"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#List of Packages and library

```{r}
library(tidyverse); library(factoextra); library(cluster) ; library(NbClust) 
library(fpc) ; library(dendroextras); library(dendextend); library(mclust) 
library(dbscan) ; library(dplyr); library(plyr); library(dataQualityR)
library(e1071) ; library(seriation); library(DT);library(arulesViz)
library(arulesCBA)
```
#Data input
```{r}
data=read.csv("https://raw.githubusercontent.com/vigneshjmurali/Statistical-Predictive-Modelling/master/Datasets/Final%20project_dataset.csv")
dim(data)
#names(data)
```

#PREPROCESSING - IMPUTATION 
The variable Field consist of factors with 260 levels which is going to affect the analysis in future. in this senario the levels are good to reduce with differrent levels of categories and revaluing them is done below

```{r}
data$field=as.character(data$field)
data$d_d_age=revalue(data$d_d_age,c("[0-1]"="1")); levels(data)
data$field=recode(data$field, "'African-American Studies/History'"="Education")
data$field=recode(data$field,"'American Studies [Masters]'"="Education")
data$field=recode(data$field,"'Applied Maths/Econs'"="Science")
data$field=recode(data$field,"'Applied Physiology & Nutrition'"="Science")
data$field=recode(data$field,"'art education'"= "Art")
data$field=recode(data$field,"'Art Education'"="Art")
data$field=recode(data$field,"'art history'"="Art")
data$field=recode(data$field,"'Art History'"="Art")
data$field=recode(data$field,"'Art History/medicine'"="Art")
data$field=recode(data$field,"'Arts Administration'"="Art")
data$field=recode(data$field,"'bilingual education'"="Education")
data$field=recode(data$field,"'Bilingual Education'"="Education")
data$field=recode(data$field,"'Biochemistry & Molecular Biophysics'"="Science")
data$field=recode(data$field,"'Biology PhD'"="Science")
data$field=recode(data$field,"'biomedical engineering'"="Engineering")
data$field=recode(data$field,"'Biomedical engineering'"="Engineering")
data$field=recode(data$field,"'Biomedical Engineering'"="Engineering")
data$field=recode(data$field,"'biomedical informatics'"="Engineering")
data$field=recode(data$field,"'Biomedical Informatics'"="Engineering")
data$field=recode(data$field,"'Business- MBA'"="Business")
data$field=recode(data$field,"'Business [Finance & Marketing]'"="Business")
data$field=recode(data$field,"'Business [MBA]'"="Business")
data$field=recode(data$field,"'Business Administration'"="Business")
data$field=recode(data$field,"'Business and International Affairs [MBA/MIA Dual Degree]'"="Business")
data$field=recode(data$field,"'BUSINESS CONSULTING'"="Business")
data$field=recode(data$field,"'business school'"="Business")
data$field=recode(data$field,"'Business School'"="Business")
data$field=recode(data$field,"'Business/ Finance/ Real Estate'"="Business")
data$field=recode(data$field,"'Business; marketing'"="Business")
data$field=recode(data$field,"'Business; Media'"="Business")
data$field=recode(data$field,"'Cell Biology'"="Science")
data$field=recode(data$field,"'Climate-Earth and Environ. Science'"="Science")
data$field=recode(data$field,"'climate change'"="Science")
data$field=recode(data$field,"'Climate Dynamics'"="Science")
data$field=recode(data$field,"'Clinical Psychology'"="Science")
data$field=recode(data$field,"'Cognitive Studies in Education'"="Education")
data$field=recode(data$field,"'Communications in Education'"="Education")
data$field=recode(data$field,"'Comparative Literature'"="Education")
data$field=recode(data$field,"'Computational Biochemsistry'"="Science")
data$field=recode(data$field,"'Computer Science'"="Engineering")
data$field=recode(data$field,"'Conservation biology'"="Science")
data$field=recode(data$field,"'Counseling Psychology'"="Education")
data$field=recode(data$field,"'Creative Writing'"="Education")
data$field=recode(data$field,"'Creative Writing - Nonfiction'"="Education")
data$field=recode(data$field,"'Creative Writing [Nonfiction]'"="Education")
data$field=recode(data$field,"'Curriculum and Teaching/Giftedness'"="Education")
data$field=recode(data$field,"'Early Childhood Education'"="Education")
data$field=recode(data$field,"'Earth and Environmental Science'"="Science")
data$field=recode(data$field,"'Economics and Political Science'"="Science")
data$field=recode(data$field,"'Economics; English'"="Education")
data$field=recode(data$field,"'Economics; Sociology'"="Education")
data$field=recode(data$field,"'Ed.D. in higher education policy at TC'"="Education")
data$field=recode(data$field,"'Education- Literacy Specialist'"="Education")
data$field=recode(data$field,"'Education Administration'"="Education")
data$field=recode(data$field,"'Education Leadership - Public School Administration'"="Education")
data$field=recode(data$field,"'Education Policy'"="Education")
data$field=recode(data$field,"'Educational Psychology'"="Education")
data$field=recode(data$field,"'Electrical Engg.'"="Engineering")
data$field=recode(data$field,"'electrical engineering'"="Engineering")
data$field=recode(data$field,"'Electrical Engineering'"="Engineering")
data$field=recode(data$field,"'ELECTRICAL ENGINEERING'"="Engineering")
data$field=recode(data$field,"'elementary education'"="Education")
data$field=recode(data$field,"'Elementary Education'"="Education")
data$field=recode(data$field,"'Elementary Education - Preservice'"="Education")
data$field=recode(data$field,"'Elementary/Childhood Education [MA]'"="Education")
data$field=recode(data$field,"'English and Comp Lit'"="Education")
data$field=recode(data$field,"'English Education'"="Education")
data$field=recode(data$field,"'Environmental Engineering'"="Engineering")
data$field=recode(data$field,"'Financial Engineering'"="Engineering")
data$field=recode(data$field,"'financial math'"="Business")
data$field=recode(data$field,"'Fundraising Management'"="Business")
data$field=recode(data$field,"'General management/finance'"="Business")
data$field=recode(data$field,"'Genetics & Development'"="Science")
data$field=recode(data$field,"'German Literature'"="Education")
data$field=recode(data$field,"'GS Postbacc PreMed'"="Medical")
data$field=recode(data$field,"'Health policy'"="Education")
data$field=recode(data$field,"'Higher Ed. - M.A.'"="Education")
data$field=recode(data$field,"'History [GSAS - PhD]'"="Education")
data$field=recode(data$field,"'History of Religion'"="Education")
data$field=recode(data$field,"'Human Rights'"="Education")
data$field=recode(data$field,"'Human Rights: Middle East'"="Education")
data$field=recode(data$field,"'Industrial Engineering'"="Engineering")
data$field=recode(data$field,"'Industrial Engineering/Operations Research'"="Engineering")
data$field=recode(data$field,"'Instructional Media and Technology'"="Engineering")
data$field=recode(data$field,"'Instructional Tech & Media'"="Engineering")
data$field=recode(data$field,"'Intellectual Property Law'"="Business")
data$field=recode(data$field,"'International affairs'"="Business")
data$field=recode(data$field,"'International Affairs'"="Business")
data$field=recode(data$field,"'international affairs - economic development'"="Business")
data$field=recode(data$field,"'International Affairs - Economic Policy'"="Business")
data$field=recode(data$field,"'International Affairs and Public Health'"="Business")
data$field=recode(data$field,"'International Affairs/Business'"="Business")
data$field=recode(data$field,"'International Affairs/Finance'"="Business")
data$field=recode(data$field,"'international affairs/international finance'"="Business")
data$field=recode(data$field,"'International Business'"="Business")
data$field=recode(data$field,"'International Development'"="Business")
data$field=recode(data$field,"'International Educational Development'"="Business")
data$field=recode(data$field,"'international finance and business'"="Business")
data$field=recode(data$field,"'International Finance; Economic Policy'"="Business")
data$field=recode(data$field,"'International Politics'"="Business")
data$field=recode(data$field,"'International Relations'"="Business")
data$field=recode(data$field,"'International Security Policy - SIPA'"="Business")
data$field=recode(data$field,"'Intrernational Affairs'"="Business")
data$field=recode(data$field,"'Japanese Literature'"="Education")
data$field=recode(data$field,"'Law and English Literature [J.D./Ph.D.]'"="Education")
data$field=recode(data$field,"'Law and Social Work'"="Education")
data$field=recode(data$field,"'MA Biotechnology'"="Science")
data$field=recode(data$field,"'MA in Quantitative Methods'"="Science")
data$field=recode(data$field,"'MA Science Education'"="Science")
data$field=recode(data$field,"'MA Teaching Social Studies'"="Science")
data$field=recode(data$field,"'marine geophysics'"="Education")
data$field=recode(data$field,"'Master in Public Administration'"="Education")
data$field=recode(data$field,"'Master of International Affairs'"="Education")
data$field=recode(data$field,"'Masters in Public Administration'"="Education")
data$field=recode(data$field,"'Masters of Industrial Engineering'"="Education")
data$field=recode(data$field,"'Masters of Social Work'"="Education")
data$field=recode(data$field,"'Masters of Social Work&Education'"="Business")
data$field=recode(data$field,"'math education'"="Business")
data$field=recode(data$field,"'math of finance'"="Business")
data$field=recode(data$field,"'Mathematical Finance'"="Business")
data$field=recode(data$field,"'Mathematics; PhD'"="Business")
data$field=recode(data$field,"'MBA - Private Equity / Real Estate'"="Business")
data$field=recode(data$field,"'MBA / Master of International Affairs [SIPA]'"="Business")
data$field=recode(data$field,"'MBA Finance'"="Business")
data$field=recode(data$field,"'Mechanical Engineering'"="Engineering")
data$field=recode(data$field,"'medical informatics'"="Medical")
data$field=recode(data$field,"'Medical Informatics'"="Medical")
data$field=recode(data$field,"'medicine and biochemistry'"="Medical")
data$field=recode(data$field,"'MFA -Film'"="Education")
data$field=recode(data$field,"'MFA  Poetry'"="Education")
data$field=recode(data$field,"'MFA Acting Program'"="Education")
data$field=recode(data$field,"'MFA Creative Writing'"="Education")
data$field=recode(data$field,"'MFA Writing'"="Education")
data$field=recode(data$field,"'Modern Chinese Literature'"="Education")
data$field=recode(data$field,"'Molecular Biology'"="Science")
data$field=recode(data$field,"'Museum Anthropology'"="Science")
data$field=recode(data$field,"'music education'"="Education")
data$field=recode(data$field,"'Music Education'"="Education")
data$field=recode(data$field,"'Neuroscience and Education'"="Education")
data$field=recode(data$field,"'Neurosciences/Stem cells'"="Education")
data$field=recode(data$field,"'Nonfiction writing'"="Education")
data$field=recode(data$field,"'NonFiction Writing'"="Education")
data$field=recode(data$field,"'Operations Research'"="Science")
data$field=recode(data$field,"'Operations Research [SEAS]'"="Science")
data$field=recode(data$field,"'Organizational Psychology'"="Science")
data$field=recode(data$field,"'Philosophy [Ph.D.]'"="Science")
data$field=recode(data$field,"'Philosophy and Physics'"="Science")
data$field=recode(data$field,"'physics [astrophysics]'"="Science")
data$field=recode(data$field,"'political science'"="Science")
data$field=recode(data$field,"'Political Science'"="Science")
data$field=recode(data$field,"'psychology and english'"="Education")
data$field=recode(data$field,"'Public Administration'"="Education")
data$field=recode(data$field,"'Public Health'"="Education")
data$field=recode(data$field,"'Public Policy'"="Education")
data$field=recode(data$field,"'Religion; GSAS'"="Education")
data$field=recode(data$field,"'School Psychology'"="Education")
data$field=recode(data$field,"'SIPA-International Affairs'"="Education")
data$field=recode(data$field,"'SIPA - Energy'"="Education")
data$field=recode(data$field,"'SIPA / MIA'"="Education")
data$field=recode(data$field,"'SOA -- writing'"="Education")
data$field=recode(data$field,"'Social Studies Education'"="Education")
data$field=recode(data$field,"'social work'"="Education")
data$field=recode(data$field,"'Social work'"="Education")
data$field=recode(data$field,"'Social Work'"="Education")
data$field=recode(data$field,"'Social Work/SIPA'"="Education")
data$field=recode(data$field,"'Sociology and Education'"="Education")
data$field=recode(data$field,"'Sociomedical Sciences- School of Public Health'"="Education")
data$field=recode(data$field,"'Speech Language Pathology'"="Education")
data$field=recode(data$field,"'Speech Languahe Pathology'"="Education")
data$field=recode(data$field,"'speech pathology'"="Education")
data$field=recode(data$field,"'Speech Pathology'"="Education")
data$field=recode(data$field,"'TC [Health Ed]'"="Education")
data$field=recode(data$field,"'teaching of English'"="Education")
data$field=recode(data$field,"'Theatre Management & Producing'"="Education")
data$field=recode(data$field,"'Undergrad - GS'"="Education")
data$field=recode(data$field,"'Urban Planning'"="Education")
data$field=recode(data$field,"'Writing: Literary Nonfiction'"="Education")
data$field=recode(data$field,"?"="Education")
data$field=recode(data$field,"Acting"="Education")
data$field=recode(data$field,"anthropology"="Science")
data$field=recode(data$field,"Anthropology"="Science")
data$field=recode(data$field,"Anthropology/Education"="Science")
data$field=recode(data$field,"Architecture"="Science")
data$field=recode(data$field,"Biochemistry"="Science")
data$field=recode(data$field,"biochemistry/genetics"="Science")
data$field=recode(data$field,"biology"="Science")
data$field=recode(data$field,"Biology"="Science")
data$field=recode(data$field,"biomedicine"="Science")
data$field=recode(data$field,"biotechnology"="Science")
data$field=recode(data$field,"Biotechnology"="Science")
data$field=recode(data$field,"business"="Business")
data$field=recode(data$field,"Business"="Business")
data$field=recode(data$field,"Business/Law"="Business")
data$field=recode(data$field,"chemistry"="Science")
data$field=recode(data$field,"Chemistry"="Science")
data$field=recode(data$field,"Classics"="Education")
data$field=recode(data$field,"Communications"="Education")
data$field=recode(data$field,"Consulting"="Education")
data$field=recode(data$field,"Ecology"="Education")
data$field=recode(data$field,"Economics"="Education")
data$field=recode(data$field,"education"="Education")
data$field=recode("Education"="Education",data$field)
data$field=recode("EDUCATION"="Education",data$field)
data$field=recode("engineering"="Engineering",data$field)
data$field=recode("Engineering"="Engineering",data$field)
data$field=recode("English"="Education",data$field)
data$field=recode("epidemiology"="Science",data$field)
data$field=recode("Epidemiology"="Science",data$field)
data$field=recode("film"="Education",data$field)
data$field=recode("Film"="Education",data$field)
data$field=recode("Finanace"="Business",data$field)
data$field=recode("Finance"="Business",data$field)
data$field=recode("Finance&Economics"="Business",data$field)
data$field=recode("Finance/Economics"="Business",data$field)
data$field=recode("french"="Business",data$field)
data$field=recode("genetics"="Science",data$field)
data$field=recode("Genetics"="Science",data$field)
data$field=recode("GSAS"="Education",data$field)
data$field=recode("History"="Education",data$field)
data$field=recode("journalism"="Education",data$field)
data$field=recode("Journalism"="Education",data$field)
data$field=recode(data$field,"law"="LAW")
data$field=recode("Law"="LAW",data$field)
data$field=recode("LAW"="LAW",data$field)
data$field=recode("Law/Business"="LAW",data$field)
data$field=recode("Marketing"="LAW",data$field)
data$field=recode("math"="Science",data$field)
data$field=recode("Math"="Science",data$field)
data$field=recode("Mathematics"="Science",data$field)
data$field=recode("MBA"="Science",data$field)
data$field=recode("medicine"="Science",data$field)
data$field=recode("Medicine"="Science",data$field)
data$field=recode("microbiology"="Science",data$field)
data$field=recode("Microbiology"="Science",data$field)
data$field=recode("money"="Science",data$field)
data$field=recode("Neurobiology"="Science",data$field)
data$field=recode("Neuroscience"="Science",data$field)
data$field=recode("nutrition"="Science",data$field)
data$field=recode("Nutrition"="Science",data$field)
data$field=recode("Nutrition/Geneticse"="Science",data$field)
data$field=recode("Nutritiron"="Science",data$field)
data$field=recode("philosophy"="Science",data$field)
data$field=recode("Philosophy"="Science",data$field)
data$field=recode("physics"="Science",data$field)
data$field=recode("Physics"="Science",data$field)
data$field=recode("Polish"="Education",data$field)
data$field=recode("psychology"="Education",data$field)
data$field=recode("Psychology"="Education",data$field)
data$field=recode("QMSS"="Education",data$field)
data$field=recode("Religion"="Education",data$field)
data$field=recode("sociology"="Education",data$field)
data$field=recode("Sociology"="Education",data$field)
data$field=recode("Statistics"="Science",data$field)
data$field=recode("Stats"="Science",data$field)
data$field=recode("TESOL"="Education",data$field)
data$field=recode("Theater"="Education",data$field)
data$field=recode("theory"="Education",data$field)
data$field=recode("working"="Education",data$field)
# Plot raw field
data$field <- tolower(data$field)
barplot(table(data$field),main = "Careers")
```

Each variable has some factor variables of different notations including "[levels of points]", and "?" here the values are imputed based on the probability of highest value noted in each variable and revalued the different notations with highest value noted in the table.

#PREPROCESSING
 
```{r}
#data$d_d_age - Renaming levels of a factor
#str(data$d_d_age)
data$d_d_age=revalue(data$d_d_age,c("[0-1]"="1"))
data$d_d_age=revalue(data$d_d_age,c("[2-3]"="3"))
data$d_d_age=revalue(data$d_d_age,c("[4-6]"="5"))
data$d_d_age=revalue(data$d_d_age,c("[7-37]"="10"))
#table(data$d_d_age)
#data$d_importance_same_race - Renaming levels of a factor
#str(data$d_importance_same_race)
data$d_importance_same_race=revalue(data$d_importance_same_race,c("[0-1]"="1"))
data$d_importance_same_race=revalue(data$d_importance_same_race,c("[2-5]"="5"))
data$d_importance_same_race=revalue(data$d_importance_same_race,c("[6-10]"="8"))
#table(data$d_importance_same_race)
##data$d_importance_same_religion - 
#str(data$d_importance_same_religion)
data$d_importance_same_religion=revalue(data$d_importance_same_religion,c("[0-1]"="1"))
data$d_importance_same_religion=revalue(data$d_importance_same_religion,c("[2-5]"="4"))
data$d_importance_same_religion=revalue(data$d_importance_same_religion,c("[6-10]"="8"))
#d_pref_o_attractive
#str(data$d_pref_o_attractive)
data$d_pref_o_attractive=revalue(data$d_pref_o_attractive,c("[0-15]"="10"))
data$d_pref_o_attractive=revalue(data$d_pref_o_attractive,c("[16-20]"="18"))
data$d_pref_o_attractive=revalue(data$d_pref_o_attractive,c("[21-100]"="75"))
#d_pref_o_sincere
#str(data$d_pref_o_sincere)
data$d_pref_o_sincere=revalue(data$d_pref_o_sincere,c("[0-15]"="10"))
data$d_pref_o_sincere=revalue(data$d_pref_o_sincere,c("[16-20]"="18"))
data$d_pref_o_sincere=revalue(data$d_pref_o_sincere,c("[21-100]"="75"))
#d_pref_o_intelligence
#str(data$d_pref_o_intelligence)
data$d_pref_o_intelligence=revalue(data$d_pref_o_intelligence,c("[0-15]"="10"))
data$d_pref_o_intelligence=revalue(data$d_pref_o_intelligence,c("[16-20]"="18"))
data$d_pref_o_intelligence=revalue(data$d_pref_o_intelligence,c("[21-100]"="75"))
#d_pref_o_funny
#str(data$d_pref_o_funny)
data$d_pref_o_funny=revalue(data$d_pref_o_funny,c("[0-15]"="10"))
data$d_pref_o_funny=revalue(data$d_pref_o_funny,c("[16-20]"="18"))
data$d_pref_o_funny=revalue(data$d_pref_o_funny,c("[21-100]"="75"))
#d_pref_o_ambitious
#str(data$d_pref_o_ambitious)
data$d_pref_o_ambitious=revalue(data$d_pref_o_ambitious,c("[0-15]"="10"))
data$d_pref_o_ambitious=revalue(data$d_pref_o_ambitious,c("[16-20]"="18"))
data$d_pref_o_ambitious=revalue(data$d_pref_o_ambitious,c("[21-100]"="75"))
#d_pref_o_shared_interests
#str(data$d_pref_o_shared_interests)
data$d_pref_o_shared_interests=revalue(data$d_pref_o_shared_interests,c("[0-15]"="10"))
data$d_pref_o_shared_interests=revalue(data$d_pref_o_shared_interests,c("[16-20]"="18"))
data$d_pref_o_shared_interests=revalue(data$d_pref_o_shared_interests,c("[21-100]"="75"))
#d_attractive_o
#str(data$d_attractive_o)
data$d_attractive_o=revalue(data$d_attractive_o,c("[0-5]"="4"))
data$d_attractive_o=revalue(data$d_attractive_o,c("[6-8]"="7"))
data$d_attractive_o=revalue(data$d_attractive_o,c("[9-10]"="9"))
#d_sinsere_o
#str(data$d_sinsere_o)
data$d_sinsere_o=revalue(data$d_sinsere_o,c("[0-5]"="4"))
data$d_sinsere_o=revalue(data$d_sinsere_o,c("[6-8]"="7"))
data$d_sinsere_o=revalue(data$d_sinsere_o,c("[9-10]"="9"))
#d_intelligence_o
#str(data$d_intelligence_o)
data$d_intelligence_o=revalue(data$d_intelligence_o,c("[0-5]"="4"))
data$d_intelligence_o=revalue(data$d_intelligence_o,c("[6-8]"="7"))
data$d_intelligence_o=revalue(data$d_intelligence_o,c("[9-10]"="9"))
#d_funny_o
#str(data$d_funny_o)
data$d_funny_o=revalue(data$d_funny_o,c("[0-5]"="4"))
data$d_funny_o=revalue(data$d_funny_o,c("[6-8]"="7"))
data$d_funny_o=revalue(data$d_funny_o,c("[9-10]"="9"))
#d_ambitous_o
#str(data$d_ambitous_o)
data$d_ambitous_o=revalue(data$d_ambitous_o,c("[0-5]"="4"))
data$d_ambitous_o=revalue(data$d_ambitous_o,c("[6-8]"="7"))
data$d_ambitous_o=revalue(data$d_ambitous_o,c("[9-10]"="9"))
#d_shared_interests_o
#str(data$d_shared_interests_o)
data$d_shared_interests_o=revalue(data$d_shared_interests_o,c("[0-5]"="4"))
data$d_shared_interests_o=revalue(data$d_shared_interests_o,c("[6-8]"="7"))
data$d_shared_interests_o=revalue(data$d_shared_interests_o,c("[9-10]"="9"))
#d_attractive_important
#str(data$d_attractive_important)
data$d_attractive_important=revalue(data$d_attractive_important,c("[0-15]"="10"))
data$d_attractive_important=revalue(data$d_attractive_important,c("[16-20]"="18"))
data$d_attractive_important=revalue(data$d_attractive_important,c("[21-100]"="75"))
#d_sincere_important
#str(data$d_sincere_important)
data$d_sincere_important=revalue(data$d_sincere_important,c("[0-15]"="10"))
data$d_sincere_important=revalue(data$d_sincere_important,c("[16-20]"="18"))
data$d_sincere_important=revalue(data$d_sincere_important,c("[21-100]"="75"))
#d_intellicence_important
#str(data$d_intellicence_important)
data$d_intellicence_important=revalue(data$d_intellicence_important,c("[0-15]"="10"))
data$d_intellicence_important=revalue(data$d_intellicence_important,c("[16-20]"="18"))
data$d_intellicence_important=revalue(data$d_intellicence_important,c("[21-100]"="75"))
#d_funny_important
#str(data$d_funny_important)
data$d_funny_important=revalue(data$d_funny_important,c("[0-15]"="10"))
data$d_funny_important=revalue(data$d_funny_important,c("[16-20]"="18"))
data$d_funny_important=revalue(data$d_funny_important,c("[21-100]"="75"))
#d_ambition_important
#str(data$d_ambtition_important)
data$d_ambtition_important=revalue(data$d_ambtition_important,c("[0-15]"="10"))
data$d_ambtition_important=revalue(data$d_ambtition_important,c("[16-20]"="18"))
data$d_ambtition_important=revalue(data$d_ambtition_important,c("[21-100]"="75"))
#d_shared_interests_important
#str(data$d_shared_interests_important)
data$d_shared_interests_important=revalue(data$d_shared_interests_important,c("[0-15]"="10"))
data$d_shared_interests_important=revalue(data$d_shared_interests_important,c("[16-20]"="18"))
data$d_shared_interests_important=revalue(data$d_shared_interests_important,c("[21-100]"="75"))
#d_attractive
#str(data$d_attractive)
data$d_attractive=revalue(data$d_attractive,c("[0-5]"="4"))
data$d_attractive=revalue(data$d_attractive,c("[6-8]"="7"))
data$d_attractive=revalue(data$d_attractive,c("[9-10]"="9"))
#d_sincere
#str(data$d_sincere)
data$d_sincere=revalue(data$d_sincere,c("[0-5]"="4"))
data$d_sincere=revalue(data$d_sincere,c("[6-8]"="7"))
data$d_sincere=revalue(data$d_sincere,c("[9-10]"="9"))
#d_intelligence
#str(data$d_intelligence)
data$d_intelligence=revalue(data$d_intelligence,c("[0-5]"="4"))
data$d_intelligence=revalue(data$d_intelligence,c("[6-8]"="7"))
data$d_intelligence=revalue(data$d_intelligence,c("[9-10]"="9"))
#d_funny
#str(data$d_funny)
data$d_funny=revalue(data$d_funny,c("[0-5]"="4"))
data$d_funny=revalue(data$d_funny,c("[6-8]"="7"))
data$d_funny=revalue(data$d_funny,c("[9-10]"="9"))
#d_ambition
#str(data$d_ambition)
data$d_ambition=revalue(data$d_ambition,c("[0-5]"="4"))
data$d_ambition=revalue(data$d_ambition,c("[6-8]"="7"))
data$d_ambition=revalue(data$d_ambition,c("[9-10]"="9"))
#d_attractive_partner
#str(data$d_attractive_partner)
data$d_attractive_partner=revalue(data$d_attractive_partner,c("[0-5]"="4"))
data$d_attractive_partner=revalue(data$d_attractive_partner,c("[6-8]"="7"))
data$d_attractive_partner=revalue(data$d_attractive_partner,c("[9-10]"="9"))
#d_sincere_partner
#str(data$d_sincere_partner)
data$d_sincere_partner=revalue(data$d_sincere_partner,c("[0-5]"="4"))
data$d_sincere_partner=revalue(data$d_sincere_partner,c("[6-8]"="7"))
data$d_sincere_partner=revalue(data$d_sincere_partner,c("[9-10]"="9"))
#d_intelligence_partner
#str(data$d_intelligence_partner)
data$d_intelligence_partner=revalue(data$d_intelligence_partner,c("[0-5]"="4"))
data$d_intelligence_partner=revalue(data$d_intelligence_partner,c("[6-8]"="7"))
data$d_intelligence_partner=revalue(data$d_intelligence_partner,c("[9-10]"="9"))
#d_funny_partner
#str(data$d_funny_partner)
data$d_funny_partner=revalue(data$d_funny_partner,c("[0-5]"="4"))
data$d_funny_partner=revalue(data$d_funny_partner,c("[6-8]"="7"))
data$d_funny_partner=revalue(data$d_funny_partner,c("[9-10]"="9"))
#d_ambitous_partner
#str(data$d_ambition_partner)
data$d_ambition_partner=revalue(data$d_ambition_partner,c("[0-5]"="4"))
data$d_ambition_partner=revalue(data$d_ambition_partner,c("[6-8]"="7"))
data$d_ambition_partner=revalue(data$d_ambition_partner,c("[9-10]"="9"))
#d_shared_interests_o
#str(data$d_shared_interests_partner)
data$d_shared_interests_partner=revalue(data$d_shared_interests_partner,c("[0-5]"="4"))
data$d_shared_interests_partner=revalue(data$d_shared_interests_partner,c("[6-8]"="7"))
data$d_shared_interests_partner=revalue(data$d_shared_interests_partner,c("[9-10]"="9"))
#d_sports
#str(data$d_sports)
data$d_sports=revalue(data$d_sports,c("[0-5]"="3"))
data$d_sports=revalue(data$d_sports,c("[6-8]"="7"))
data$d_sports=revalue(data$d_sports,c("[9-10]"="9"))
#d_tvsports
#str(data$d_tvsports)
data$d_tvsports=revalue(data$d_tvsports,c("[0-5]"="3"))
data$d_tvsports=revalue(data$d_tvsports,c("[6-8]"="7"))
data$d_tvsports=revalue(data$d_tvsports,c("[9-10]"="9"))
#d_exercise
#str(data$d_exercise)
data$d_exercise=revalue(data$d_exercise,c("[0-5]"="3"))
data$d_exercise=revalue(data$d_exercise,c("[6-8]"="7"))
data$d_exercise=revalue(data$d_exercise,c("[9-10]"="9"))
#d_dining
#str(data$d_dining)
data$d_dining=revalue(data$d_dining,c("[0-5]"="3"))
data$d_dining=revalue(data$d_dining,c("[6-8]"="7"))
data$d_dining=revalue(data$d_dining,c("[9-10]"="9"))
#d_museums
#str(data$d_museums)
data$d_museums=revalue(data$d_museums,c("[0-5]"="3"))
data$d_museums=revalue(data$d_museums,c("[6-8]"="7"))
data$d_museums=revalue(data$d_museums,c("[9-10]"="9"))
#d_art
#str(data$d_art)
data$d_art=revalue(data$d_art,c("[0-5]"="3"))
data$d_art=revalue(data$d_art,c("[6-8]"="7"))
data$d_art=revalue(data$d_art,c("[9-10]"="9"))
#d_hiking
#str(data$d_hiking)
data$d_hiking=revalue(data$d_hiking,c("[0-5]"="3"))
data$d_hiking=revalue(data$d_hiking,c("[6-8]"="7"))
data$d_hiking=revalue(data$d_hiking,c("[9-10]"="9"))
#d_gaming
#str(data$d_gaming)
data$d_gaming=revalue(data$d_gaming,c("[0-5]"="3"))
data$d_gaming=revalue(data$d_gaming,c("[6-8]"="7"))
data$d_gaming=revalue(data$d_gaming,c("[9-10]"="9"))
#d_clubbing
#str(data$d_clubbing)
data$d_clubbing=revalue(data$d_clubbing,c("[0-5]"="3"))
data$d_clubbing=revalue(data$d_clubbing,c("[6-8]"="7"))
data$d_clubbing=revalue(data$d_clubbing,c("[9-10]"="9"))
#d_reading
#str(data$d_reading)
data$d_reading=revalue(data$d_reading,c("[0-5]"="3"))
data$d_reading=revalue(data$d_reading,c("[6-8]"="7"))
data$d_reading=revalue(data$d_reading,c("[9-10]"="9"))
#d_tv
#str(data$d_tv)
data$d_tv=revalue(data$d_tv,c("[0-5]"="3"))
data$d_tv=revalue(data$d_tv,c("[6-8]"="7"))
data$d_tv=revalue(data$d_tv,c("[9-10]"="9"))
#d_theater
#str(data$d_theater)
data$d_theater=revalue(data$d_theater,c("[0-5]"="3"))
data$d_theater=revalue(data$d_theater,c("[6-8]"="7"))
data$d_theater=revalue(data$d_theater,c("[9-10]"="9"))
#d_movies
#str(data$d_movies)
data$d_movies=revalue(data$d_movies,c("[0-5]"="3"))
data$d_movies=revalue(data$d_movies,c("[6-8]"="7"))
data$d_movies=revalue(data$d_movies,c("[9-10]"="9"))
#d_concerts
#str(data$d_concerts)
data$d_concerts=revalue(data$d_concerts,c("[0-5]"="3"))
data$d_concerts=revalue(data$d_concerts,c("[6-8]"="7"))
data$d_concerts=revalue(data$d_concerts,c("[9-10]"="9"))
#d_music
#str(data$d_music)
data$d_music=revalue(data$d_music,c("[0-5]"="3"))
data$d_music=revalue(data$d_music,c("[6-8]"="7"))
data$d_music=revalue(data$d_music,c("[9-10]"="9"))
#d_shopping
#str(data$d_shopping)
data$d_shopping=revalue(data$d_shopping,c("[0-5]"="3"))
data$d_shopping=revalue(data$d_shopping,c("[6-8]"="7"))
data$d_shopping=revalue(data$d_shopping,c("[9-10]"="9"))
#d_yoga
#str(data$d_yoga)
data$d_yoga=revalue(data$d_yoga,c("[0-5]"="3"))
data$d_yoga=revalue(data$d_yoga,c("[6-8]"="7"))
data$d_yoga=revalue(data$d_yoga,c("[9-10]"="9"))
#d_expected_happy_with_sd_peple
#str(data$d_expected_happy_with_sd_people)
data$d_expected_happy_with_sd_people=revalue(data$d_expected_happy_with_sd_people,c("[0-4]"="2"))
data$d_expected_happy_with_sd_people=revalue(data$d_expected_happy_with_sd_people,c("[5-6]"="6"))
data$d_expected_happy_with_sd_people=revalue(data$d_expected_happy_with_sd_people,c("[7-10]"="8"))
#d_expected_num_interested_in_me
#str(data$d_expected_num_interested_in_me)
data$d_expected_num_interested_in_me=revalue(data$d_expected_num_interested_in_me,c("[0-3]"="2"))
data$d_expected_num_interested_in_me=revalue(data$d_expected_num_interested_in_me,c("[10-20]"="15"))
data$d_expected_num_interested_in_me=revalue(data$d_expected_num_interested_in_me,c("[4-9]"="7"))
#d_expected_num_matches
#str(data$d_expected_num_matches)
data$d_expected_num_matches=revalue(data$d_expected_num_matches,c("[0-2]"="1"))
data$d_expected_num_matches=revalue(data$d_expected_num_matches,c("[3-5]"="4"))
data$d_expected_num_matches=revalue(data$d_expected_num_matches,c("[5-18]"="11"))
#d_like
#str(data$d_like)
data$d_like=revalue(data$d_like,c("[0-5]"="3"))
data$d_like=revalue(data$d_like,c("[6-8]"="7"))
data$d_like=revalue(data$d_like,c("[9-10]"="9"))
#d_guess_partner_liked
#str(data$d_guess_prob_liked)
data$d_guess_prob_liked=revalue(data$d_guess_prob_liked,c("[0-4]"="2"))
data$d_guess_prob_liked=revalue(data$d_guess_prob_liked,c("[5-6]"="5.5"))
data$d_guess_prob_liked=revalue(data$d_guess_prob_liked,c("[7-10]"="8.5"))
#table(data$age) # Checking for the maxi levels in the data for variable age
data$age=revalue(data$age,c("?"="27")) #Imputing the "?" of the age variable to 27 which is listed higher
#revalue age_o
data$age_o=revalue(data$age_o,c("?"="27"))
#table(data$age_o)
#revalue importance_same_race
data$importance_same_race=revalue(data$importance_same_race,c("?"="1"))
#table(data$importance_same_race)
#revalue importance_same_religion
data$importance_same_religion=revalue(data$importance_same_religion,c("?"="1"))
#table(data$importance_same_religion)
#revalue pref_o_attractive
data$pref_o_attractive=revalue(data$pref_o_attractive,c("?"="15"))
#table(data$pref_o_attractive)
#revalue pref_o_sincere
#table(data$pref_o_sincere)
data$pref_o_sincere=revalue(data$pref_o_sincere,c("?"="20"))
#revalue pref_o_intellignece
data$pref_o_intelligence=revalue(data$pref_o_intelligence,c("?"="20"))
#table(data$pref_o_intelligence)
#revalue pref_o_funny
data$pref_o_funny=revalue(data$pref_o_funny,c("?"="20"))
#table(data$pref_o_funny)
#revalue pref_o_ambitious
data$pref_o_ambitious=revalue(data$pref_o_ambitious,c("?"="10"))
#table(data$pref_o_ambitious)
#revalue pref_o_shared_interests
data$pref_o_shared_interests=revalue(data$pref_o_shared_interests,c("?"="10"))
#table(data$pref_o_shared_interests)
#revalue attractive _o
data$attractive_o=revalue(data$attractive_o,c("?"="6"))
#table(data$attractive_o)
#revalue sinsere_o
data$sinsere_o=revalue(data$sinsere_o,c("?"="7"))
#table(data$sinsere_o)
#revalue intelligence_o
data$intelligence_o=revalue(data$intelligence_o,c("?"="8"))
#table(data$intelligence_o)
#revalue funny_o
data$funny_o=revalue(data$funny_o,c("?"="7"))
#table(data$funny_o)
#revalue ambitous_o
data$ambitous_o=revalue(data$ambitous_o,c("?"="7"))
#table(data$ambitous_o)
#revalue shared_interests_o
data$shared_interests_o=revalue(data$shared_interests_o,c("?"="5"))
#table(data$shared_interests_o)
#revalue attractive_important
data$attractive_important=revalue(data$attractive_important,c("?"="20"))
#table(data$attractive_important)
#revalue sincere _important
data$sincere_important=revalue(data$sincere_important,c("?"="20"))
#table(data$sincere_important)
#revalue intellicence_important
data$intellicence_important=revalue(data$intellicence_important,c("?"="20"))
#table(data$intellicence_important)
#revalue funny_important
data$funny_important=revalue(data$funny_important,c("?"="20"))
#table(data$funny_important)
#revalue ambtition important
data$ambtition_important=revalue(data$ambtition_important,c("?"="10"))
#table(data$ambtition_important)
#revalue shared_interests_important
data$shared_interests_important=revalue(data$shared_interests_important,c("?"="10"))
#table(data$shared_interests_important)
#revalue attractive
data$attractive=revalue(data$attractive,c("?"="7"))
#table(data$attractive)
#revalue sincere
data$sincere=revalue(data$sincere,c("?"="9"))
#table(data$sincere)
#revalue intelligence
#table(data$intelligence)
data$intelligence=revalue(data$intelligence,c("?"="8"))
#revalue funny
#table(data$funny)
data$funny=revalue(data$funny,c("?"="9"))
#revalue ambition
#table(data$ambition)
data$ambition=revalue(data$ambition,c("?"="8"))
#revalue sincere_partner
#table(data$sincere_partner)
data$sincere_partner=revalue(data$sincere_partner,c("?"="9"))
#revalue intelligence_partner
#table(data$intelligence_partner)
data$intelligence_partner=revalue(data$intelligence_partner,c("?"="8"))
#revalue funny_partner
#table(data$funny_partner)
data$funny_partner=revalue(data$funny_partner,c("?"="6"))
#revalue ambition_partner
#table(data$ambition_partner)
data$ambition_partner=revalue(data$ambition_partner,c("?"="7"))
#revalue shared_interests partern
#table(data$shared_interests_partner)
data$shared_interests_partner=revalue(data$shared_interests_partner,c("?"="5"))
#revalue sports
#table(data$sports)
data$sports=revalue(data$sports,c("?"="8"))
#revalue tvsports
#table(data$tvsports)
data$tvsports=revalue(data$tvsports,c("?"="1"))
#revalue exercise
#table(data$exercise)
data$exercise=revalue(data$exercise,c("?"="8"))
#revalue dining
#table(data$dining)
data$dining=revalue(data$dining,c("?"="8"))
#musemus
#table(data$museums)
data$museums=revalue(data$museums,c("?"="8"))
#art
#table(data$art)
data$art=revalue(data$art,c("?"="8"))
#hiking
#table(data$hiking)
data$hiking=revalue(data$hiking,c("?"="8"))
#gaming
#table(data$gaming)
data$gaming=revalue(data$gaming,c("?"="1"))
#clubbing
#table(data$clubbing)
data$clubbing=revalue(data$clubbing,c("?"="8"))
#reading
#table(data$reading)
data$reading=revalue(data$reading,c("?"="9"))
#tv
#table(data$tv)
data$funny=revalue(data$funny,c("?"="5"))
#theater
#table(data$theater)
data$theater=revalue(data$theater,c("?"="7"))
#movies
#table(data$movies)
data$movies=revalue(data$movies,c("?"="8"))
#concerts
#table(data$concerts)
data$concerts=revalue(data$concerts,c("?"="8"))
#music
#table(data$music)
data$music=revalue(data$music,c("?"="8"))
#shopping
#table(data$shopping)
data$shopping=revalue(data$shopping,c("?"="7"))
#yoga
#table(data$yoga)
data$yoga=revalue(data$yoga,c("?"="1"))
#expected_happy_with sd_people
#table(data$expected_happy_with_sd_people)
data$expected_happy_with_sd_people=revalue(data$expected_happy_with_sd_people,c("?"="5"))
#expected_num_intereste_in me
#table(data$expected_num_interested_in_me)
data$expected_num_interested_in_me=revalue(data$expected_num_interested_in_me,c("?"="2"))
#expected num of matches
#table(data$expected_num_matches)
data$expected_num_matches=revalue(data$expected_num_matches,c("?"="2"))
#d_expected happy with sd people
#table(data$d_expected_happy_with_sd_people)
#d_expected num inte in me
#table(data$d_expected_num_interested_in_me)
#d_exp_num_matchs
#table(data$d_expected_num_matches)
#like
#table(data$like)
data$like=revalue(data$like,c("?"="7"))
#guess_prob_like
#table(data$guess_prob_liked)
data$guess_prob_liked=revalue(data$guess_prob_liked,c("?"="5"))
#d_like
#table(data$d_like)
#d_guess_prob like
#table(data$d_guess_prob_liked)
#met
#table(data$met)
data$met=revalue(data$met,c("?"="1"))
#decision
#table(data$decision)
#decision_o
#table(data$decision_o)
#table(data$match)
#race
data$race=revalue(data$race,c("?"="European/Caucasian-American"))
#race_o
data$race_o=revalue(data$race_o,c("?"="European/Caucasian-American"))
#tv
data$tv=revalue(data$tv,c("?"="6"))
#attractive partner
data$attractive_partner=revalue(data$attractive_partner,c("?"="6"))
```

After the data has been revalued the unwanted variable is dropped and writed the new imputed data into a CSV file to process in the PYTHON FOR CLASSIFICATION

```{r}
speed<-data[,-c(3,8,9,15,108,109)]
dim(speed)
#write.csv(speed,"data2.csv")
```

#=========================================================================================

```{r}
speed[1:10,1:10]
matching<-sum(speed$match=='0')/8378
nonmatch<-sum(speed$match=='1')/8378
dat<-data.frame(match=factor(c("matching","nonmatch")),percent=c(nonmatch,matching))
ggplot(data=dat,aes(x=match,y=percent,fill=match))+geom_bar(color="black",stat="identity")
```
#=========================================================================================

#ASSOCIATON RULES - WITH ACTUAL DATASET

```{r}
speed.arules<-data[,-c(108,109)]
dim(speed.arules)
#write.csv(speed.arules,"arules.csv")
library(arules);library(arulesViz); library(arulesCBA)
speed.arules[,names(speed.arules)]<-lapply(speed.arules[,names(speed.arules)],factor)
speed.arules<-as(speed.arules,"transactions")
itemFrequencyPlot(speed.arules[, itemFrequency(speed.arules) > 0.5], cex.names = 0.6)
rules1 <- apriori(data = speed.arules , parameter = list( supp = 0.001 , conf = 0.7) , appearance = list(default = "lhs" , rhs = "match=1") )
rules1<-sort(rules1 , decreasing = TRUE , by = 'lift')
## Sorting rules based on confidence,printing the rules
inspect(rules1[1:10])
## Ploting the generated rules
plot(rules1, measure=c("support", "lift"), shading="confidence")
#reduce the number of rules here by filtering out all rules with a low confidence score.
head(quality(rules1))
#subrules <- rules1[quality(rules1)$confidence > 0.8]
#inspect(rules1[1:50])
#plot(subrules, method="matrix3D", measure="lift", control=list(reorder=TRUE))
#Re-running association rules with support = 0.0012 and confidence = 0.9
## Association rule generation
#rules2 <- apriori(data = speed.arules , parameter = list( supp = 0.0012 , conf = 0.9) , appearance = list(default = "lhs" , rhs = "match=1") )
## Sorting rules based on confidence
#rules2 <- sort(rules2 , decreasing = TRUE , by = 'confidence')
## Printing the rules
#inspect(rules2)
#plot(rules2, measure=c("support", "lift"), shading="confidence")
```
#ASSOCIATON RULES WITH IMPUTED DATA
```{r}
data2.arules<-data[,-c(1,2,9,108,109,119,117,121,122,110,111,112,113,114,115)]
dim(data2.arules)
#write.csv(speed.arules,"arules.csv")
library(arules);library(arulesViz); library(arulesCBA)
data2.arules[,names(data2.arules)]<-lapply(data2.arules[,names(data2.arules)],factor)
data2.arules<-as(data2.arules,"transactions")
itemFrequencyPlot(data2.arules[, itemFrequency(data2.arules) > 0.5], cex.names = 0.6)
data2.rules1 <- apriori(data = data2.arules , parameter = list( supp = 0.001 , conf = 0.95) , appearance = list(default = "lhs" , rhs = "match=0") )
data2.rules1<-sort(data2.rules1 , decreasing = TRUE , by = 'lift')
## Sorting rules based on confidence,printing the rules
inspect(data2.rules1[1:20])
## Ploting the generated rules
plot(data2.rules1,method="graph")
#reduce the number of rules here by filtering out all rules with a low confidence score.
```

```{r}
speed.arules.disc<-as.data.frame(lapply(speed.arules[1:120],function(x)discretize(x,categories=2)))
```

#ASSOCIATION RULES - PERSONAL SIDE ASSOCIATION(ONESIDE)
```{r}
oneside=read.csv("https://raw.githubusercontent.com/vigneshjmurali/Statistical-Predictive-Modelling/master/Datasets/attributes%20of%20data.csv")
oneside<-oneside[,-c(61)]
dim(oneside)
#View(oneside)
oneside[,names(oneside)]<-lapply(oneside[,names(oneside)],factor)
oneside<-as(oneside,"transactions")
itemFrequencyPlot(oneside[, itemFrequency(oneside) > 0.5], cex.names = 0.6)

rules1.oneside <- apriori(data = oneside , parameter = list( supp = 0.001 , conf = 0.9) , appearance = list(default = "lhs" , rhs = "match=0") )
rules1<-sort(rules1.oneside , decreasing = TRUE , by = 'lift')
## Sorting rules based on confidence,printing the rules
inspect(rules1[1:10])
```
#ASSOCIATION RULES - PARTNER SIDE ASSOCIATION(OTHERSIDE)
```{r}
partnerside=read.csv("https://raw.githubusercontent.com/vigneshjmurali/Statistical-Predictive-Modelling/master/Datasets/attributes%20of%20data1.csv")
partnerside<-partnerside[,-c(61)]
dim(partnerside)
#View(oneside)
partnerside[,names(partnerside)]<-lapply(partnerside[,names(partnerside)],factor)
partnerside<-as(partnerside,"transactions")
itemFrequencyPlot(partnerside[, itemFrequency(partnerside) > 0.5], cex.names = 0.6)

rules1.partnerside <- apriori(data = partnerside , parameter = list( supp = 0.001 , conf = 0.9) , appearance = list(default = "lhs" , rhs = "match=0") )
rules1.partnerside<-sort(rules1.partnerside , decreasing = TRUE , by = 'lift')
## Sorting rules based on confidence,printing the rules
inspect(rules1.partnerside[1:10])

#BY REMOVING D_AGE 
partnerside=read.csv("https://raw.githubusercontent.com/vigneshjmurali/Statistical-Predictive-Modelling/master/Datasets/attributes%20of%20data1.csv")
partnerside<-partnerside[,-c(61)]
dim(partnerside)
#View(oneside)
partnerside[,names(partnerside)]<-lapply(partnerside[,names(partnerside)],factor)
partnerside<-as(partnerside,"transactions")
itemFrequencyPlot(partnerside[, itemFrequency(partnerside) > 0.5], cex.names = 0.6)

rules1.partnerside <- apriori(data = partnerside , parameter = list( supp = 0.001 , conf = 0.9) , appearance = list(default = "lhs" , rhs = "match=0") )
rules1.partnerside<-sort(rules1.partnerside , decreasing = TRUE , by = 'lift')
## Sorting rules based on confidence,printing the rules
inspect(rules1.partnerside[1:10])
```

#ASSOCIATION RULES - SPECIFIC INTEREST ARULES
```{r}
SP=read.csv("https://raw.githubusercontent.com/vigneshjmurali/Statistical-Predictive-Modelling/master/Datasets/SPECIFIC%20INTEREST_ARULES.csv")
#oneside<-oneside[,-c(61)]
dim(SP)
#View(oneside)
SP[,names(SP)]<-lapply(SP[,names(SP)],factor)
SP<-as(SP,"transactions")
itemFrequencyPlot(SP[, itemFrequency(SP) > 0.5], cex.names = 0.6)

rules1.SP <- apriori(data = SP , parameter = list( supp = 0.001 , conf = 0.9) , appearance = list(default = "lhs" , rhs = "match=0") )
rules1.SP<-sort(rules1.SP , decreasing = TRUE , by = 'lift')
## Sorting rules based on confidence,printing the rules
inspect(rules1.SP[1:10])

```

#============================================================================================

#CLUSTER ANALYSIS - ACTUAL DATASET
```{r}
data.clus=read.csv("https://raw.githubusercontent.com/vigneshjmurali/Statistical-Predictive-Modelling/master/Datasets/data2.csv")
dim(data.clus)
data.clus<-data.clus[,-c(1,115,116,117)]
dim(data.clus)
```
#CLUSTERING FOR WHOLE DATASET

```{r}
data.clus.s=scale(data.clus)
data.clus.pca=prcomp(data.clus)
data.clus.pca$rotation[1:5,1:5]
data.clus.sd=data.clus.pca$sdev
data.clus.var=data.clus.pca$sdev^2 
data.clus.var[1:10]
# Proportion of variance 
pve=data.clus.var/sum(data.clus.var) 
which.max(cumsum(pve)[cumsum(pve)<0.85])
cumsum(pve[11]) 
fviz_screeplot(data.clus.pca,ncp=11,choice="eigenvalue")
plot(cumsum(pve),xlab="Principal Component", ylab="Cumulative Proportion of variance explained",ylim=c(0,1),type='b')
biplot(data.clus.pca,arrow.len=0)
data.clus_Classes<- factor(data.clus$match)
plot(main="Different Groups",data.clus.pca$x[,1:11],col=data.clus_Classes)

# Choosing the principle components as new variables based on the total variance
data.clus_new=data.clus.pca$x[,1:11] 
data.clus_new.s=scale(data.clus_new) 
actualfit=kmeans(data.clus_new,5,nstart=50)
plotcluster(data.clus_new,actualfit$cluster)

# OPTIMAL NUMBER OF CLUSTERS - (1) WSS, (2) Silhouette, (3) Gap_stat, (4) NbClust # For PC 1 to PC 11
set.seed(10)
fviz_nbclust(data.clus_new,kmeans,method="wss") # Using elbow method - wss
fviz_nbclust(data.clus_new,kmeans,method="gap_stat")
fviz_nbclust(data.clus_new,kmeans,method="silhouette")
#NBCLUST
data.clus.nbclust<-data.clus_new %>% #Using NbClust 
 scale() %>% 
  NbClust(distance="euclidean",min.nc=5,max.nc=15,method="complete",index="all")
#MCLUST
data.clus.mclust<-Mclust(data.clus_new.s) 
summary(data.clus.mclust)
fviz_mclust(data.clus.mclust,"BIC",palette="jco")
fviz_mclust(data.clus.mclust,"classification",geom="point",pointsize=1.5, palette="jco")
# fazzy clustering
gap<-kmeans(data.clus_new.s,centers=7,iter.max=100,nstart=25)
fviz_cluster(gap,data=data.clus_new.s,ellipse.type="convex",palette="jco",repel=TRUE,ggtheme=theme_minimal())
#Hierarchial Clustering with K=2 
hc.ward=hclust(dist(data.clus_new,method="euclidean"),method="ward.D2") #Dendogram 
plot(hc.ward, main="Complete Linkage",xlab="",cex=.9) #Drawing dendogram with red borders around the clusters 
rect.hclust(hc.ward,k=7,border="red")
#groups2=cutree(hc.ward,7)#Cut Tree into 2 clusters 
#clusplot(data.clus_new,groups2,color=TRUE, shade = TRUE, labels=2, lines=0, main='Group segments')
```

#CLUSTER ANALYSIS - ATTRIBUTES OF DATA - ONE PERSON SIDE(PERSONAL SIDE DATA)
```{r}
attributes=read.csv("https://raw.githubusercontent.com/vigneshjmurali/Statistical-Predictive-Modelling/master/Datasets/attributes%20of%20data.csv")
dim(attributes)
data.attri<-attributes[,-c(1,5,9,61,62)] ; dim(data.attri)
data.attri.mat<-as.matrix(data.attri)
data.attri.pca<-prcomp(data.attri.mat)
data.attri.pca$rotation[1:5,1:5]
data.attri.sd=data.attri.pca$sdev; data.attri.var=data.attri.pca$sdev^2 #To compute variance 
data.attri.var[1:5] ; pve=data.attri.var/sum(data.attri.var) ; cumsum(pve[1:10])
fviz_screeplot(data.attri.pca,np=60,choice="eigenvalue")
plot(cumsum(pve),xlab="Principal Component", ylab="Cumulative Proportion of variance explained",ylim=c(0,1),type='b')
which.max(cumsum(pve)[cumsum(pve)<0.90]) ; biplot(data.attri.pca)
#Choosing the principle components as new variables
data.attri.new=data.attri.pca$x[,1:18] ; data.attri.new.s=scale(data.attri.new)

#K means clustering
set.seed(10) 
fviz_nbclust(data.attri.new,kmeans,method="wss")
fviz_nbclust(data.attri.new,kmeans,method="silhouette")
fviz_nbclust(data.attri.new,kmeans,method="gap_stat")
#NBCLUST - use unless you want to have to wait for long time
data.attri.nbclust<-data.attri.new %>% #Using NbClust 
  scale() %>% 
  NbClust(distance="euclidean",min.nc=2,max.nc=15,method="complete",index="all")
#fuzzy kmeans
set.seed(10) 
km_11_2.fit=kmeans(data.attri.new,4,nstart=50)
plotcluster(data.attri.new,km_11_2.fit$cluster)
fviz_cluster(km_11_2.fit,data=data.attri.new,ellipse.type="convex",palette="jco",ggtheme=theme_minimal())

#MCLUST
data.attri.fit<-Mclust(data.attri.new.s[,0:18]) 
summary(data.attri.fit)
fviz_mclust(data.attri.fit,"BIC",palette="jco")
fviz_mclust(data.attri.fit,"classification",geom="point",pointsize=1.5, palette="jco")
fviz_mclust(data.attri.fit,"uncertainty", palette="jco")

#data.attri.group<-data.frame(data.attri.new,km_11_8.fit$cluster)
#write.csv(data.attri.group$km_11_8.fit.cluster,"attri_group_8clus.csv")
```

#CLUSTER ANALYSIS - ATTRIBUTES OF DATA - OTHER PERSON SIDE(PARTNER SIDE DATA) 
```{r}
attributes1=read.csv("https://raw.githubusercontent.com/vigneshjmurali/Statistical-Predictive-Modelling/master/Datasets/attributes%20of%20data1.csv")
dim(attributes1)
data.attri1<-attributes1[,-c(1,5,9,61,62)]
dim(data.attri1)
data.attri1.mat<-as.matrix(data.attri1)
data.attri1.pca<-prcomp(data.attri1.mat)
data.attri1.pca$rotation[1:5,1:5]
data.attri1.sd=data.attri1.pca$sdev; data.attri1.var=data.attri1.pca$sdev^2 #To compute variance 
data.attri1.var[1:5]
pve=data.attri1.var/sum(data.attri1.var) ; cumsum(pve[1:10])
fviz_screeplot(data.attri1.pca,np=10,choice="eigenvalue")
plot(cumsum(pve),xlab="Principal Component", ylab="Cumulative Proportion of variance explained",ylim=c(0,1),type='b')
which.max(cumsum(pve)[cumsum(pve)<0.90])


#biplot(data.attri.pca)
#Choosing the principle components as new variables

data.attri1.new=data.attri1.pca$x[,1:8]
data.attri1.new.s=scale(data.attri1.new)
#K means clustering
set.seed(10) 
fviz_nbclust(data.attri1.new,kmeans,method="wss") #k=4
fviz_nbclust(data.attri1.new,kmeans,method="silhouette") # k=9
fviz_nbclust(data.attri1.new,kmeans,method="gap_stat") #k=5

#NBCLUST - use unless you want to have to wait for long time
data.attri1.nbclust<-data.attri1.new %>% #Using NbClust 
  scale() %>% 
  NbClust(distance="euclidean",min.nc=2,max.nc=15,method="complete",index="all")

#fuzzy kmeans
set.seed(10)
km_11_2_attri1.fit=kmeans(data.attri1.new,8,nstart=50)
plotcluster(data.attri1.new,km_11_2_attri1.fit$cluster)
fviz_cluster(km_11_2_attri1.fit,data=data.attri1.new,ellipse.type="convex",palette="jco",ggtheme=theme_minimal())

#MCLUST
data.attri1.fit<-Mclust(data.attri1.new.s[,0:8]) 
summary(data.attri1.fit)
data.attri1.fit$modelName 
fviz_mclust(data.attri1.fit,"BIC",palette="jco")
fviz_mclust(data.attri1.fit,"classification",geom="point",pointsize=1.5, palette="jco")
fviz_mclust(data.attri1.fit,"uncertainty", palette="jco")

data.attri1.group<-data.frame(data.attri1.new,km_11_8_attri1.fit$cluster)
#write.csv(data.attri1.group$km_11_8_attri1.fit.cluster,"attri_group1_8clus.csv")

```
#==============================================================================
#COMPARISON OF THE TARGET AFTER CLUSTERING

```{r}
comparison=read.csv("https://raw.githubusercontent.com/vigneshjmurali/Statistical-Predictive-Modelling/master/Datasets/clustervsactual%20match.csv")
barplot(comparison)
str(comparison)
dim(comparison)
cor(comparison$cluster.match,comparison$actual.match)
hist(comparison$cluster.match)
hist(comparison$actual.match)
a<-with(comparison,which(comparison$cluster.match!=comparison$actual.match))
b<-data.clus$match==0
#######
#check the response
par(mfrow=c(1,2))
notmatching<-sum(comparison$actual.match==0)/nrow(comparison)
matching<-sum(comparison$actual.match==1)/nrow(comparison)
dat <- data.frame(
  matching_status_actual.match = factor(c("notmatching","matching"), levels=c("notmatching","matching")),percent = c( notmatching,matching))
ggplot(data=dat, aes(x=matching_status_actual.match, y=percent, fill=matching_status_actual.match)) +
geom_bar(colour="black", stat="identity")
############
#check the response
notmatching<-sum(comparison$cluster.match==0)/nrow(comparison)
matching<-sum(comparison$cluster.match==1)/nrow(comparison)

dat <- data.frame(
  matching_status_cluster.match = factor(c("notmatching","matching"), levels=c("notmatching","matching")),percent = c( notmatching,matching))
ggplot(data=dat, aes(x=matching_status_cluster.match, y=percent, fill=matching_status_cluster.match)) +
geom_bar(colour="black", stat="identity")


```


#======================================================================================
#THE END
#=======================================================================================
